\documentclass[12pt,a4paper,norsk]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{units}
\usepackage{dirtytalk}
\usepackage{enumerate}
\usepackage{graphicx}

\input{front_page}

\renewcommand{\thesection}{§\arabic{section}}

\begin{document}


\section{The Association's Name}

The name of the association is \say{UiO Gaming}.


\section{Purpose}

UiO Gaming's purpose is to promote gaming, e-sports, board games and other gaming-related interests/cultures at UiO. In addition, we wish to create a social environment that facilitates all forms of activity around games. The association aims to organize game nights, tournaments, LAN and other gaming-related activities open to anyone who is interested.



\section{Organizational Structure}

UiO Gaming is a voluntary student organization at the University of Oslo and was founded September 11th, 2020. The association is politically and religiously independent.
\\
\\
The association is an independent legal entity with members and is independently owned. This means that neither members nor any others have a claim to its capital and assets, and are not liable to its debts.



\section{Members}

A membership is valid from January 1st to December 31st and costs NOK 50. A minimum of 75\% of the association's members must be enrolled students at an SiO-registered educational institution or former students at the University of Oslo, and at least 50\% of the members must enrolled at UiO the present semester. The association has an age limit of 18 years old and members must fulfill one of these two requirements: be an enrolled student or under 35 years of age.



\section{Membership Rights and Duties}

All members have the right to participate in the general assembly and have the right to vote. They are eligible for positions in positions of trust such as the board of the association. The members are obliged to comply with decisions made by the general assembly.
\\
\\
Members who cause the association financial losses in the form of fines or sanctions as a result of actions that can easily be avoided are made to be financially responsible for these themselves. The board decide whether or not the member(s) in question shall be held liable or not with a minimum \nicefrac{2}{3} majority vote.


\section{Honorary membership}

Every semester the board can give out up to 2 honorary memberships to people that have made an extraordinary effort to the benefit of the association. Honorary members are given a lifetime membership in the association. Honorary members are exempt from the rules defined in §4.



\section{The General Assembly}

The general assembly is the association's highest body.
\\
\\
The general assembly must be held at least once per semester. It must be held by the end of December in the autumn semester and by the end of June during the spring semester.
\\
\\
The general assembly take decisions by a simple majority. No member has more than one vote and voting cannot take place by proxy.
\\
\\
An extraordinary general assembly can be held if a minimum of \nicefrac{1}{3} of the members require it or the board deems it necessary.
\\
\\
An announcement of the general assembly must fulfilled at least two weeks before the meeting. All meeting documents must be available to association members at least one week before the meeting.
\\
\\
Amendments to the statutes that are to be voted on at the general assembly must be handed in to the board at least one week before the meeting, and changes can only take place with a \nicefrac{2}{3} majority vote for the change.


\section{The Role of The General Assembly}

The general assembly shall

\begin{itemize}
    \item review and approve the board's/leader's report(s)
    \item review and approve accounting record(s) for the previous semester
    \item approve a budget for the upcoming semester
    \item process any proposals for changes
    \item decide the membership fee
    \item elect an election committee
    \item elect the board
\end{itemize}



\section{Election}

A new board is elected at the ordinary general assembly. Each board member is elected for one term at a time. An election period encompasses the time between two ordinary general assemblies.
\\
\\
The leader and deputy leader are elected for two terms. The deputy leader is elected at the autumn general assembly and the leader is elected during the spring general assembly.
\\
\\
All elections at the general assembly, if no other proposal are decided upon, are held by a written vote. If no one obtains at least half of the votes, a new vote shall be held between the two candidates who received the most votes in the first round. In the event of a tie, a new election is held. If there then is another tie, the elected person is chosen through a lottery.
\\
\\
In the case where a position is not filled during the general the assembly, the board can be given the power to supplement itself by a \nicefrac{2}{3} majority vote at a board meeting. In the event of an extraordinary general assembly, the person in question can be challenged for their position by a \nicefrac{2}{3} majority vote.



\section{The Election Committee}

The election committee is elected at the general assembly following a recommendation from the board, and must put forward proposals for candidates for all other positions of trust to be elected at the general assembly. Members of the election committee who themselves becomes a candidate for other positions of trust, are obliged to resign from the election committee. That is, unless the person in question gives a written notice to the election committee and propose that they are not suitable for the position.


\section{The Board}

The board consists of five or seven people. In addition to the regular board members, the general assembly can elect up to 5 deputy board members. A minimum of 50\% of the board's members must be enrolled students at UiO.
\\
\\
The board has the following mandatory positions:
\begin{itemize}
    \item Leader
    \begin{itemize}
        \item Responsible for organizing and leading board meetings. Other tasks include communication with third parties, partners, faculty and others. They have the legal right to sign documents on the behalf of the association. It is the leader's job to make sure that all members of the board upholds the association's purpose and that they execute the tasks of their elected positions. Finally, the leader is responsible to maintain the association's reputation.
    \end{itemize}

    \item Deputy Leader
    \begin{itemize}
        \item Executes the role of leader if they are absent. They are the secretary at board meetings and are responsible for organizing the general assembly.
    \end{itemize}

    \item Financial Manager
    \begin{itemize}
        \item Responsible for the healthy financial operation of the association. Presents budgets and accounts at the general assembly. Responsible for the accounting of all transactions to and from the association's bank account. They are responsible to follow up on all financial matters and duties, and inform the board on an ongoing basis about the current economic state of the association.
    \end{itemize}
\end{itemize}

The board can only make decisions when at least \nicefrac{1}{2} of the board members are present. Decisions are made by a simple majority. In the case of a tie, the leader can cast a second vote.


\section{Motion of no confidence}
\begin{enumerate}[a)]
    \item The association's members can hold a vote of no confidence against board members or other positions of trust elected in accordance to §9.
    \item A vote of no confidence will be held at an extraordinary general assembly, requirements of which are mentioned in §7, or at an ordinary general assembly if which is held within two weeks.
    \item The vote of no confidence is passed with a \nicefrac{2}{3} active majority
    \item In the case where a vote of no confidence is passed the general assembly have the right to hold an election for the now empty position that lasts until the next general assembly. The general assembly can also let the board to fill the role themselves.
\end{enumerate}



\section{The right of signature}

The association's leader, or the deputy leader in the case of absence, has the right of signature and can sign contracts on the behalf of the association  between third parties that is legally binding in any shape or form.


\section{Economy}

The association's funds must only be used in accordance with the association's purpose.
\\
\\
There must always be a budget and account for the association's funds, with accompanying annexes. The budget and accounts are reviewed and approved at the general assembly. The accounts and the budget are prepared for one calendar year at a time.
\\
\\
Payments shall always be approved by the leader, or in case of absence the deputy leader, and the financial manager.
\\
\\
When voting on financial investments, a \nicefrac{2}{3} majority is needed on the board.



\section{Discord}

The Discord server \say{UiO Gaming} shall be used as a communication channel for members. Ownership of the server is given to a user managed jointly by the leader and deputy leader. Further administration of the server is performed by the board.



\section{Disbandment}

The association can be dissolved when \nicefrac{2}{3} of the general assembly votes for it. Matters of disbandment must be reported within the general deadlines of the general assembly. Upon termination, the association's funds and assets will be given to another suitable student association with the same purpose, decided upon by the general assembly.
\\
\\
No member has a claim to the association's assets or a share of them.



\section{Ethical Guidelines}

\begin{itemize}
    \item EQUIALITY AND INCLUSION:
        All members of the association shall show respect for all people regardless of age, sex or gender identity, religion, sexual oriention, functional ability, social status, ethnicity or political views. UiO Gaming condemns all forms of discrimination, harassment or bullying. We shall all treat each other with respect and avoid all types of communication, use of words, action and treatment of others that can be interpreted as offensive, harassing, discriminatory or uncomfortable.
    
    \item RESPECT FOR OTHERS' BOUNDARIES:
        UiO Gaming shall be a safe association where an individual's integrity and boundaries are respected. Sexual harassment, sexually transgressive behavior and sexual assault is not accepted.

    \item HONESTY AND TRANSPARENCY:
    The board of UiO Gaming shall be transparent about its decisions. All meeting notes and decisions should be open to the public if there isn't any special reason to not publish it. The board shall act with honesty and no ill intent.

    \item AWARNESS OF ROLE AND POWER DYNAMICS:
    The board of UiO Gaming shall be aware of its power and the dynamic between them and other members. They shall not abuse the trust they have gained as a member of the board.
\end{itemize}



\section{Exclusion}

UiO Gaming has the right to exclude members who violate the association's purpose, statutes or ethical guidelines laid down in §17. In the case of a potential exclusion it must be dealt with at an extraordinary general assembly or a special exclusion meeting held by the board between them and any affected parties. The member in question must be given the opportunity to defend themselves in the meeting. The exclusion can be passed with a \nicefrac{2}{3} active majority at the general assembly or exclusion meeting. 
\\
\\
In the event of exclusion, the association deprives the member of all rights and membership benefits, and the person concerned also loses the membership's financial obligations and claims to the association. The member who has been excluded is entitled to a refund of the membership fee. They have the opportunity to appeal the decision on the exclusion, with a deadline of two weeks. The board can, on a later occasion, pardon the member with a \nicefrac{2}{3} active majority.



\section{Ethics and Reporting Protocols}

The association shall, to the furthest extent possible, consider the ethical impact as well as the impact on the social environment into account when planning activities. In the event of unfortunate situations related to the association and/or its activities, there should be protocols in place to report the situation in question. The board is responsible for handling these reports.
\\
\\
There should be an up-to-date report protocol and ethical guidelines that are known to all members.



\section{Sanctions}

If a member breaks Norwegian law, the association's statutes or ethical guidelines, the board can sanction the member in question. Sanctions include, but is not limited to: warnings, temporary suspension of member's rights, or in some cases subject to permanent exclusion from the association. All sanctions must be voted upon by the board with a minimum \nicefrac{2}{3} majority vote.


\end{document}
